---
title: "GMAT II"
author: "Eduardo Flores"
date: "August 7, 2015"
output: pdf_document
---
# Quant
##Temas
### **Number Theory**

- **GCF**: Sets...{1,2,3,4} & {1,2} .:. {1*2} es GCF

```{r eval = FALSE}
    subset(unique(Set1), unique(Set1) %in% unique(Set2))
```
  
- **LCM**: Sets...{1,2,3,4} & {1,2} .:. {1,2,3,4} es LCM
```{r eval = FALSE}
   unique(c(Set1, Set2))
```


- Digits; 
  + 1234.567
  + 1 - THOUSANDS
  + 2 - HUNDREDS
  + 3 - TENS
  + 4 - UNITS
  + 5 - TENTHS
  + 6 - HUNDREDTHS
  + 7 - THOUSANDTHS 

### **Exponents and Roots**

- Siempre te van a poner diferentes exponentes/bases, debes; 
  1. Romper en pedazos (ejemplo: $5^{21}*4^{11}$ => $5^{21}*2^{11}*2^{11}$ => $5^{21}*2^{22}$)
  2. Juntar los parecidos con otros (como rompiste a pedazos mas pequeños posibles (es como sacar el LCM))
  3. "Mochar" si la variable que buscas está arriba ($5^{4n} = 5^{8}$ "mochas a" $4n = 8$) y encontrar "n"


### Probability


### Combinations and Permutations


### **Plane Geometry**


### **Coordinate Geometry**

- "p" **intersects** x-axis .:. y = 0 (vice-versa con y)


### 3D Geometry (volume)


### **Functions**

For which of the following functions is f(a+b)=f(b)+f(a) for all positive numbers a and b?
  A. f(x)=x^2 
  B. f(x)=x+1 
  C. f(x)=√x 
  D. f(x)=2/x 
  E. f(x)=-3x



### Statistics
### **(x+y) and (x-y)**
### Mixture formulas
 - Pregunta; "How many liters of pure alcohol must be added to a 100-liter solution that is 20 percent alcohol in order to produce a solution that is 25 percent alcohol?"
 
|Lo que tenemos (% y Q)           | A lo que quiero llegar |   nueva solución |
|:--------------------------------|:-----------------------|:--------------------|
|alcohol puro (% = 100%, Q = x)   |                        |abs(25-20) = 5       |
|                                 | % = 25%, Q = 20 +x     |                     |
|solución hoy (% = 20%, Q = 100)  |                        |abs(100-25) = 75     |

1. Que busco? la "Q" de alcohol puro (tambien es x)...
2. Resto en "cruz", leo horizontal; 
 - Alcohol puro: 5, 
 - Solucion hoy: 75
3. Esto nos dice que por cada 75 unidades de solución, tenemos que tener 5 de alcohol puro (lo lees directo). (En ratio da, 15:1). 
4. Como la solución que tengo ya tiene 100 litros, tengo que agregarle 5 litros por cada 75 que tiene (o 1 por 15, simplificado). 
5. 100/75*5 = 100/15 = 20/3

### **Fractions, decimals (% increase/decrease)**
### Absolute values
### **Ratios, fractions of universe**
### Conversions dimensional analysis
### Groups

- Con 2: T = G1 + G2 - B + N
- Con 3: T = G1 + G2 + G3 - () - 2*() + N

### Compounded or simple interest
### **Scientific Notation**


- 10^6 = un melón; 10^9 = un billon

### Proportionality
### Critical Zone (0<x<1)
### **Zonal Trap**
### Sequences and patterns

- Recuerda: la suma de una serie consecutiva = media*n... 

### Pyramids, spaces
### Max-min, logical progression
### **Work Problem**
### **Distance Pie**
### Summations
### **Factoring roots**
### Inequalities
### Caracol/Fidel's Cigar

##Teoría Essencial (Machete)
### Shapes


1. Lados; c **debe** ser > |a-b| **and** c < |a+b|
  + Si te dan de lados: $a=3$ y $b=4$  
      *  .:. |a-b| < c < |a+b| .:. 1 < c < 7


2. Triangulos; 
  + 2 lados iguales = isoceles (perfecto = 45º, 45º y 90º = lados(1,1,$sqrt{2}$))
  + todos iguales = equilatero
  + Triangulo "revienta" = 30º-60º-90 = lados(1,$sqrt{3}$,2=hypotenusa)
  + **OB**tuse: 1 angulo > 90º 
  + a**cute**: todos < 90º


3. Tripletes;
  + {1, 2, $\sqrt(3)$} 
  + {3, 4, 5}
  + {4, 12, 13}
  + {7, 24, 25}


4. Formas irregulares; 
  + lados = 180(n-2)/n
  

5. Square if; 
  + **A**ll sides "="
  + **A**ll diagonals igual *or* bisect
  + **A**ll angles = 90º
  

6. Circulos: 
  + $pi$ =-ish $22/7$ 

### Numbers
- Primes: 

    + **SOLO** positivos, 
    + **UNICO** even es el 2, 
    + **TODOS MENOS** 2 y 5 acaban en 1,3,7 o 9. 
    + **SI ES MAYOR A 3:** regla 6n-1 ó 6n+1:
```{r eval = FALSE}
    prime <- function(n){
      if(n>3 && n>0){} else {stop("mayor a 3 y 0")}
      
      test1<- (n-1)/6 
      test2<- (n+1)/6
      # si no tienen decimal (remainder)
      # or (cualquiera de las condiciones)
      if(test1 == round(test1,0) | test2 == round(test2,0)){
        return("Prime")
      }else{return("Not Prime")}
    }
```
- Even-odds


|Resta y sum|E|O
|:--------|:-------|:---------|
|E|e|o|
|O|o|e|


|Mult|E|O
|:--------|:-------|:---------|
|E|e|e|
|O|e|o|


|div(abajo arriba)|E|O
|:--------|:-------|:---------|
|E|?|e|
|O|?|o|


- Reciprocos; 
(a)*(b)==1 .:. b es reciproco de a

****

\newpage


#Verbal
##Argument types
### General to specific
### Specific to general
### Negation, Inverse
### Cause and effect
### Analogy or comparison (correlation)
### Paradoxical
### Conclusion based on studies/survey
### Circular/continuos
### Appeal to emotion
### Explicit vs implicit
### Negative assumption
### If and only if
### Deny the premise
### Back door argument

